---
output:
  html_document:
    keep_md: yes
---
Skeleton Report 1
=================================================
This report covers the analyses used in the ZZZ project (Marcus Mark, PI).

<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of two directories.-->
```{r, echo=F, message=F} 
# cat("Working directory: ", getwd())
  library(knitr)
  opts_knit$set(root.dir='../../')  #Don't combine this call with any other chunk -especially one that uses file paths.
```

<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# cat("Working directory: ", getwd())
opts_chunk$set(
  results    = 'show', 
  comment    = NA, 
  tidy       = FALSE,
  fig.width  = 6.5, 
  fig.height = 4, 
  fig.path   = 'figure_raw/'
)
# dpi = 400,
# out.width = "650px", #This affects only the markdown, not the underlying png file.  The height will be scaled appropriately.

echoChunks <- FALSE
options(width=120) #So the output is 50% wider than the default.
read_chunk("./analysis/report_1/report_1.R") #This allows knitr to call chunks tagged in the underlying *.R file.
```

<!-- Load the sources.  Suppress the output when loading sources. --> 
```{r load_sources, echo=echoChunks, message=FALSE}
```

<!-- Load 'sourced' R files.  Suppress the output when loading packages. --> 
```{r load_packages, echo=echoChunks, message=FALSE}
```

<!-- Load any global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare_globals, echo=echoChunks, results='show', message=FALSE}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r, echo=echoChunks, message=FALSE}
#Put presentation-specific code in here.  It doesn't call a chunk in the codebehind file.
```

<!-- Load the datasets.   -->
```{r load_data, echo=echoChunks, results='show', message=FALSE}
```

<!-- Tweak the datasets.   -->
```{r tweak_data, echo=echoChunks, results='show', message=FALSE}
```

## Notes

**Note 1**: The current report covers `r nrow(ds)` cars, with `r nlevels(ds$CarburetorCountF)` possible values for `CarburetorCount`.

**Note 2**: The Seattle track's phluguerstometer was producing flaky negative values; it's measurements have been dropped.

# Marginals
```{r marginals, echo=echoChunks, message=TRUE}
```

# Scatterplots
```{r scatterplots, echo=echoChunks, message=TRUE}
```

# Models
```{r models, echo=echoChunks, message=TRUE}
```

# Questions
## Unanswered Questions
 1. What does `VS` stand for?  How was it measured?
 1. Where the cars at the Philly track measured with the same phluguerstometer and the Cleveland track?
 
## Answered Questions
 1. The Seattle track's phluguerstometer was producing flaky negative values; it's measurements have been dropped.

# Session Information
For the sake of documentation and reproducibility, the current report was rendered on a system using the following software.

```{r session_info, echo=FALSE}
cat("Report rendered by", Sys.info()["user"], "at", strftime(Sys.time(), "%Y-%m-%d, %H:%M %z"))
sessionInfo()
```
