---
title: "Cognitive Longitudinal Outcomes --PDSA Cycle 3"
output:
  flexdashboard::flex_dashboard:
    # orientation: rows
    vertical_layout: fill
    # css: ../common/style-cqi-cycle-4.css  
    # theme: cosmo
    theme: journal
---

<!-- Replace the flexdashboard entry above with this, to produce our conventional knitr report. -->
<!-- html_document: -->
<!--   keep_md: yes -->
<!--   toc: yes -->
<!--   toc_float: true -->
<!--   number_sections: true -->


<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of three directories.-->
```{r, echo=F, message=F}
# cat("Working directory: ", getwd())
library(knitr)
library(flexdashboard)
opts_knit$set(root.dir = '../../')  #Don't combine this call with any other chunk -especially one that uses file paths.
```

<!-- Set the report-wide options, and point to the external code file. -->
```{r set-options, echo=F}
# cat("Working directory: ", getwd())
report_render_start_time <- Sys.time()
opts_chunk$set(
  results      = 'show',
  comment      = NA,
  tidy         = FALSE,
  # dpi        = 400,
  # out.width  = "650px", #This affects only the markdown, not the underlying png file.  The height will be scaled appropriately.
  fig.width    = 6,
  fig.height   = 6,
  fig.path     = 'figure-dashboard-png/'
)

echo_chunks    <- FALSE #Toggle for debugging.
message_chunks <- FALSE #Toggle for debugging.
options(width = 100) #So the output is 25% wider than the default.
read_chunk("./analysis/dashboard-1/dashboard-1.R") #This allows knitr to call chunks tagged in the underlying *.R file.
```

<!-- Load 'sourced' R files.  Suppress the output when loading sources. -->
```{r load-sources, echo=echo_chunks, message=message_chunks}
```

<!-- Load packages, or at least verify they're available on the local machine.  Suppress the output when loading packages. -->
```{r load-packages, echo=echo_chunks, message=message_chunks}
```

<!-- Load any global functions and variables declared in the R file.  Suppress the output. -->
```{r declare-globals, echo=echo_chunks, results='show', message=message_chunks}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. -->
```{r rmd-specific, echo=echo_chunks, message=message_chunks}
# Put presentation-specific code in here.  It doesn't call a chunk in the codebehind file.
#   It should be rare (and used cautiously), but sometimes it makes sense to include code in Rmd
#   that doesn't live in the codebehind R file.
```

<!-- Load the datasets.   -->
```{r load-data, echo=echo_chunks, results='show', message=message_chunks}
```

<!-- Tweak the datasets.   -->
```{r tweak-data, echo=echo_chunks, results='show', message=message_chunks}
```

Headline
=============================================

<!-- The documentation page has two columns.  The test on the left, and the headline graph on the right. -->
This dashboard helps facilitate the CQI analyses VIHA E.C.R. (early cognitive recline) project.

Overall {.tabset data-width=300}
---------------------------------------------

<!-- left column -->
### Notes
1. The current report covers `r scales::comma(nrow(ds))` total subject-event records for `r dplyr::n_distinct(ds$county)` unique counties (`r paste(sort(unique(ds$county)), collapse=", ")`).
1. The year of collection ranges from `r min(ds$year, na.rm=T)` to  `r max(ds$year, na.rm=T)`.
1. The selected county is `r county_name_focus` (id value `r county_id_focus`).

{.tabset}
---------------------------------------------

<!-- unnamed right column -->
```{r headline-graph, echo=echo_chunks, results='asis', message=message_chunks}
```

Tables
=============================================

<!-- The documentation page has a single column. -->
<!-- Numerical representation of the previous graphs.  Click the tabs below to cycle between the summaries.  Tables are searchable and sortable. -->

{.tabset}
---------------------------------------------

### Tables - County-Year
```{r tables-county-year, echo=echo_chunks, message=message_chunks}
```

### Tables - County

```{r tables-county, echo=echo_chunks, message=message_chunks}
```


### Tables - Annotation

```{r tables-annotation, echo=echo_chunks, message=message_chunks}
```


Graphs
=============================================

<!-- The documentation page has a single column. -->
<!-- A program's monthly values are plotted on top of the background of other programs in the model.-->

{.tabset}
---------------------------------------------

```{r spaghetti, echo=echo_chunks, message=message_chunks, results='asis', fig.height=10, fig.width=20}
```


Marginals
=============================================
<!-- The marginals page has a single column. -->

{.tabset}
---------------------------------------------

```{r marginals, echo=echo_chunks, message=message_chunks, results='asis'} 
```

Documentation
=============================================
<!-- The documentation page has a single column. -->

{.tabset}
---------------------------------------------

### Explanation -Current PDSA

#### SMART Aim
By implementing plans for self-care activities with established clients, primary caregivers will see a mean score reduction of at least 4 points on the ECR after 4 months of self-care activities by Dec 1, 2018.

#### Measures 

* **Outcome**: Parent Stress
    * Pre- and Post- Parent Stress Scale score change
    
* **Process**: Completed Resiliency Plans
    * *Numerator*: Count of clients who completed their designated self-care activity
    * *Denominator*: Count of clients with a visist in a given week
    
* **Disruptor**: Cultural issues preventing participation, toxic stress, family catastrophe

#### Spaghetti Notes

* **To be added**:
    * Post score plots
    * Pre-post comparisons
    * Splitting out new clients from old clients to see if differences are more or less prominent

* **Mean PSS Scores - Pre**: 
    * Each blue dot represents a single client's PSS score on the pre measure
    * The orange dots (connected by the red line) represent the mean PSS score for all clients on a given week.
    * Dot size is proportional to the number of clients who had a pre-PSS score.

* **Stress Activity - Success**: 
    * *Numerator*: Number of clients who indicated having completed their self-care activity
    * *Denominator*: All clients who responded to the self-care question (Yes/No to self-care)
    * *Dot size*: The dot size is proportional to the number of clients who responded to that question on a given week.

#### Resources

* [Current PDSA](https://docs.google.com/document/d/1IcwCCkr1EkoeBJpEKdF2v-E0gKI6wGacCv9oZU1CE7I/edit#) (This is accessible only to CQI participants.)

<!-- The dashboard documentation that's common to all reports. Unfortunately, the working directory is the Rmd directory, to the repo root. -->

### Explanation -All CQI Dashboards

```{r, child = "../common/dashboard/documentation-all-dashboards-1.Rmd"}
```

### Glossary

```{r, child = "../common/dashboard/documentation-glossary-1.Rmd"}
```

### Tips

```{r, child = "../common/dashboard/documentation-tips-1.Rmd"}
```

### Config

```{r, child = "../common/dashboard/documentation-config-1.Rmd"}
```
